---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggsegAal

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegAal/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegAal/actions/workflows/R-CMD-check.yaml)
[![r-universe](https://ggsegverse.r-universe.dev/badges/ggsegAal)](https://ggsegverse.r-universe.dev/ggsegAal)
<!-- badges: end -->

AAL Atlases for the ggsegverse Ecosystem.

## Installation

```{r, eval = FALSE}
# From r-universe
install.packages("ggsegAAL", repos = "https://ggsegverse.r-universe.dev")

# From GitHub
# install.packages("remotes")
remotes::install_github("ggsegverse/ggsegAal")
```

## Atlases
### aal

Automated Anatomical Labeling parcellation (Tzourio-Mazoyer et al., 2002).

```{r aal}
library(ggsegAAL)
plot(aal())
```

### aal2

AAL2 parcellation (Rolls et al., 2015).

```{r aal2}
plot(aal2())
```

### aal3_cortical

AAL3 cortical parcellation (Rolls et al., 2020).

```{r aal3_cortical}
plot(aal3_cortical())
```

### aal3_subcortical

AAL3 subcortical parcellation.

```{r aal3_subcortical}
plot(aal3_subcortical())
```

### aal3_cerebellum

AAL3 cerebellar parcellation.

```{r aal3_cerebellum}
plot(aal3_cerebellum())
```
## Data source

FreeSurfer fsaverage5 annotations.

- **Reference**: Tzourio-Mazoyer et al. (2002) [doi:10.1006/nimg.2001.0978](https://doi.org/10.1006/nimg.2001.0978)
- **Date obtained**: 2021-10-15
